Music Classification Using Convolutional Neural Networks

### 2019-12-15 docs/paper.tex
add future improvements
merge

@@

>>>>

	\section{The dataset}

	We wanted to have a great vatiety of song samples in large quantity.
	The first dataset we took into account is the \textit{Million Song Dataset} \cite{million}.
	The sheer number of samples was quite promissing, but it turned out to be overwhelming.
	Not to mention the fact that it contained numerous pieces of information that we did not need, like the authors,
	the release year and other different identifiers for database use. 
	It needed a lot of time just to extract the necessary information we need, which would make the extension 
	of the used dataset unnecessarily time consuming.

	Our second option was the GTZAN \cite{gtzan_art} dataset used in the \textit{Musical genre classification of audio signals} \cite{gtzan}.
	It suited our needs and it covered samples from 10 clearly distinct music genres, 100 tracks each.
	As for the length of the songs, the dataset contained 30 second long samples from different parts of the songs.
	An analysis done by Bob L. Strum \cite{gtzan_anal} describes more precisely the capacity of this dataset.

@@

    \section{Future Improvements}

    There are many ways the solution could be improved. Our plans include

    \begin{itemize}
        \item augmenting the dataset by time-stretching (and squeezing) and splitting the 30 second
        samples using slightly overlapping windows
        \item experimenting with different network architectures
        \item applying \emph{Hyperparameter Optimization}
        \item maybe searching for network architectures using experimental solutions like \emph{AutoML}
    \end{itemize}
